---
title: "ezmaps"
author: "Ace Mejia-Sanchez, Amira Singh, & Anu Zaman"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
package: "`r packageVersion('ezmaps')`"
vignette: >
  %\VignetteIndexEntry{ezmaps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r, echo=FALSE, results="hide", warning=FALSE}
suppressPackageStartupMessages({
  library(ezmaps)
})
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", warning=FALSE, message=FALSE, eval=TRUE)
```

# Introduction

We created this package to facilitate the tidying and creating visualizations for exploratory analysis of geo-spatial data for beginners in R. This package helps create the following: point maps, choropleth maps, cartograms, and hexbin maps. 


## Packages

There are lots of packages used across our functions, they are all gathered below:
  
* [leaflet](https://CRAN.R-project.org/package=leaflet)

NOT DONE: List all packages used in your functions, including palettes.


# Functions & How to Use Them

## pointmap()

To plot a map using the `pointmap` function, there are five required user inputs:

1. data: The data set 

2. longitude_var: The variable containing longitude values

3. latitude_var: The variable containing latitude values

4. set_longitude: The approximate longitude value of the region to center the map on (i.e. city, state, country)

5. set_latitude: The approximate latitude value of the region to center the map on (i.e. city, state, country)

In addition to these inputs are others which allow for different markers, palettes, popups, etc. 

For example if we want to plot a point map using circle markers with a particular palette and a popup we would do the following:

```{r,fig.width=9,fig.height=9}
library(ezmaps)
pointmap(data = crash_data,
                  longitude_var = crash_data$lon,
                  latitude_var = crash_data$lat,
                  set_longitude = -71.110558,
                  set_latitude = 42.3736,
                  popups = crash_data$crash_date,
                  user_pal = c("#003f5c", "#2f4b7c","#665191",
                               "#a05195","#d45087","#f95d6a",
                               "#ff7c43","#ffa600"),
                  user_var = crash_data$year)
```


## choropleth()

NOT DONE

```{r,fig.width=9,fig.height=9}
library(ezmaps)
```


## cartogram()

NOT DONE

```{r,fig.width=9,fig.height=9}
library(ezmaps)
```

## hexbin()

NOT DONE

```{r,fig.width=9,fig.height=9}
library(ezmaps)
```

## generate_hexbin()

NOT DONE

```{r,fig.width=9,fig.height=9}
library(ezmaps)
```


# Session Info
```{r sessionInfo}
sessionInfo()
```

