---
title: "ezmaps"
author: "Ace Mejia-Sanchez, Amira Singh, & Anu Zaman"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
package: "`r packageVersion('ezmaps')`"
vignette: >
  %\VignetteIndexEntry{ezmaps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r, echo=FALSE, results="hide", warning=FALSE}
suppressPackageStartupMessages({
  library(ezmaps)
})
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", warning=FALSE, message=FALSE, eval=TRUE)
```

# Introduction

We created this package to facilitate the tidying and creating visualizations for exploratory analysis of geo-spatial data in R for beginners. This package helps create the following: point maps, choropleth maps, cartograms, and hexbin maps. 


## Packages

We use several packages across our functions, listed below:
  
* [cartogram](https://CRAN.R-project.org/package=cartogram)

* [geogrid](https://cran.r-project.org/web/packages/geogrid/)

* [graphics](https://search.r-project.org/R/refmans/graphics/html/00Index.html)

* [leaflet](https://CRAN.R-project.org/package=leaflet/)

* [sf](https://cran.r-project.org/web/packages/sf/)

* [tigris](https://cran.r-project.org/web/packages/tigris/)

* [tmap](https://cran.r-project.org/web/packages/tmap/)

* [viridis](https://cran.r-project.org/web/packages/viridis/index.html)


# How to Use the Functions

## Creating point maps with pointmap()

A point map plots geographic latitude/longitude data on a map, typically to visualize the spatial distribution of individual entities, objects, events, etc. at a high level of granularity. Points can be colored according to the values of a variable.

This function is a wrapper for the `leaflet()` function from the `leaflet` package. We recommend beginners use `ezmaps::pointmap()` to gain familiarity with `leaflet::leaflet()` before viewing the documentation and vignettes of that package for additional functionalities. To plot an interactive map using the `ezmaps::pointmap()` function, there are five required user inputs:

1. `data`: The dataset 

2. `longitude_var`: The variable containing longitude values

3. `latitude_var`: The variable containing latitude values

4. `set_longitude`: The approximate longitude value of the region to center the map on (i.e. city, state, country)

5. `set_latitude`: The approximate latitude value of the region to center the map on (i.e. city, state, country)

There are also optional inputs for different markers, palettes, popups: `popups`, `icon_filepath`, `icon_width`, `icon_height`, `zoom_min`, `zoom_max`, `set_zoom`, `map_tile`, `point_color`, `point_radius`, `point_inopacity`, `point_outopacity`, `user_pal`, `user_var`. 

For example, if we want to plot a point map using circle markers with a particular palette and a popup we would do the following:

```{r,fig.width=9,fig.height=9}
library(ezmaps)
pointmap(data = crash_data,
                  longitude_var = crash_data$lon,
                  latitude_var = crash_data$lat,
                  set_longitude = -71.110558,
                  set_latitude = 42.3736,
                  popups = crash_data$crash_date,
                  user_pal = c("#003f5c", "#2f4b7c","#665191",
                               "#a05195","#d45087","#f95d6a",
                               "#ff7c43","#ffa600"),
                  user_var = crash_data$year)
```

## Creating choropleth maps with choropleth()

A choropleth map uses color to show how a variable varies across a geographic area or to show the level of variability within a region, at varying levels of granularity.

To plot an interactive map using the `ezmaps::choropleth()` function, there are four required user inputs:

1. `data`: The dataset

2. `variable`: The variable encoded to the shade of the colors of the regions

3. `geometry`: The geometry variable of the dataset

4. `palette`: The palette used to determine the colors of the different regions

There are also optional user inputs, such as `alpha`, that can be added to personalize the map. The map is interactive, includes pop-ups and zoom options, and also has the Viridis palette as a default palette for colorblind accessibility.  

For example, if we want to observe differences in the United States population of different states by the differences in shades of the regions, we would do the following:

```{r,fig.width=9,fig.height=9}
library(ezmaps)
choropleth(data = states, 
           variable = "Population", 
           geometry = geometry, 
           palette = "viridis")
```


## Creating cartograms with cartogram()

A cartogram distorts the geometry of geographic regions based on a variable, at varying levels of granularity. Regions can remain uncolored, be colored by the same variable, or be colored by a different variable. 

This function is a wrapper for the `cartogram_cont()` function from the `cartogram` package. We recommend beginners use `ezmaps::cartogram()` to gain familiarity with `cartogram::cartogram_cont()` and `sf` type data before viewing the documentation and vignettes of that package for additional functionalities. To plot an interactive map using the `ezmaps::cartogram()` function, there are five required user inputs:

1. `data`: The dataset

2. `weight`: The variable encoded to the size or distortion of the region

3. `variable`: The variable corresponding to the palette; can be the same as `weight`

4. `geometry`: The geometry variable of the dataset

5. `palette`: The palette used to determine the colors of the different regions

There are also optional user inputs such as `base`, which controls whether the map contains the base map. To exclude the base map, the user can input `base` = NULL; to include the base map, the user can input any integer, such as `base` = 1. The map is interactive, includes pop-ups and zoom options, and also has the Viridis palette as a default palette for colorblind accessibility.  

For example, if we want to plot a cartogram for the percentage of the United States population that eats a daily serving of vegetables each day, relative to the population of the region, we would do the following: 

```{r,fig.width=9,fig.height=9}
library(ezmaps)
cartogram(data = states, 
          weight = "Population", 
          variable = "Vegetables", 
          geometry = geometry, 
          palette = "viridis",
          base = 1)
```

## Creating hexbin maps with hexbin()

An issue that can arise with choropleth maps is that regions are different sizes, which can lead to the visual misconception that the importance or weight of each region is determined by its geographic area, rather than by the respective value of the variable being mapped. On choropleth maps, larger areas receive more visual emphasis. One method of mitigating this issue is to use a hexbin mapping technique.

The hexbin map is a size-adjusted choropleth map that allows the user to compare how a variable differs by region through differences in color, at varying levels of granularity. The user also inputs a column for labeling the different regions, since the regions are necessarily indistinguishable by shape or size. 

This function simplifies the process of creating hexbin maps using the `geogrid` package. It plots a hexagonal grid fitted to the original geometry of the geographic regions of interest. Each hexagon represents one region and is labeled accordingly. The hexagons are colored according to the values of a variable. To plot an interactive map using the `ezmaps::hexbin()` function, there are five required user inputs:

1. `data`: The dataset

2. `fill`: Variable encoded to fill of the hexagons

3. `labels`: Variable encoded to labels/abbreviations for the regions represented by the hexagons

4. `palette`: The palette used to determine the colors of the hexagons

5. `geometry`: Variable that gives geometry/multipolygon data

There are also optional user inputs such as `seed`, which gives the number of the corresponding seed map generated by `tesselate()` that the user has determined best represents the original geography. The map is interactive, includes pop-ups and zoom options, and also has the Viridis palette as a default palette for colorblind accessibility.  

For example, if we want to plot a hexbin map for the percentage of the United States population that eats a daily serving of vegetables each day, we would do the following: 

```{r,fig.width=9,fig.height=9}
library(ezmaps)
hexbin(data = states,
                fill = "Vegetables",
                labels = "STUSPS",
                geometry = geometry,
                palette = "viridis")
```

## Using tessellate() to choose base grid for hexbin maps

This optional function allows the user to view multiple configurations of hexagon tessellations ("seed maps") fitted to the geographical multipolygon data of interest. While this is function is not required to create hexbins with `ezmaps::hexbin()`, we recommend using `ezmaps::tessellate()` to identify the seed map of best fit for use with `ezmaps::hexbin()`. 

Necessarily, the user must call `tessellate()` before `hexbin()`. The user can then input one of the seed maps created using `tessellate()` as the base grid used by the `hexbin()` function using the `hexbin(seed)` argument.  

To create seed maps using the `ezmaps::tessellate()` function, there are three required inputs:

1. `data`: The dataset

2. `geometry`: Variable that gives geometry/multipolygon data

3. `n`: Variable that gives number of seed maps to generate

For example, if we want to generate 6 seed maps for the (contiguous) United States, we would do the following: 

We first generate the 6 seed maps using the `tessellate(n)` argument.

```{r,fig.width=9,fig.height=9}
library(ezmaps)
tessellate(data = states, geometry = geometry, n = 6)
```

Then, if we wanted to choose seed map 6 as the base grid used by the `hexbin()` function, we would use the `hexbin(seed)` argument.  

```{r}
library(ezmaps)
hexbin(data = states,
       fill = "Population",
       labels = "STUSPS",
       geometry = geometry,
       palette = "viridis",
       seed = 6)
```


# Other notes

Note that the current version of `hexbin()` is limited to contiguous regions. We recommend subsetting dataset geometry variables to contain only contiguous regions.

The dataset containing the geometry/simple feature variable can be transformed before being inputted as an argument. Specifically, the projections or coordinates can be altered using `sf::st_transform`.

# Session Info
```{r sessionInfo}
sessionInfo()
```

