---
title: "ezmaps"
author: "Ace Mejia-Sanchez, Amira Singh, & Anu Zaman"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
package: "`r packageVersion('ezmaps')`"
vignette: >
  %\VignetteIndexEntry{ezmaps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r, echo=FALSE, results="hide", warning=FALSE}
suppressPackageStartupMessages({
  library(ezmaps)
})
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", warning=FALSE, message=FALSE, eval=TRUE)
```

# Introduction

NOT DONE

## Packages

There are lots of packages used across our functions, they are all gathered below:
  
* [leaflet](https://CRAN.R-project.org/package=leaflet)

NOT DONE: List all packages used in your functions, including palettes.


# Functions & How to Use Them

## pointmap()

To plot a map using the `pointmap` function, there are three required user inputs:

1. data

2. longitude_var

3. latitude_var

4. set_longitude

5. set_latitude

For example if we want to plot a point map using circle markers with a particular palette along with supplying a popup:

```{r,fig.width=9,fig.height=9}
library(ezmaps)
pointmap(data = crash_data,
                  longitude_var = crash_data$lon,
                  latitude_var = crash_data$lat,
                  set_longitude = -71.110558,
                  set_latitude = 42.3736,
                  popups = crash_data$crash_date,
                  user_pal = c("#003f5c", "#2f4b7c","#665191",
                               "#a05195","#d45087","#f95d6a",
                               "#ff7c43","#ffa600"),
                  user_var = crash_data$year)
```


## choropleth()

NOT DONE

```{r,fig.width=9,fig.height=9}
library(ezmaps)
```


## cartogram()

NOT DONE

```{r,fig.width=9,fig.height=9}
library(ezmaps)
```

## hexbin()

NOT DONE

```{r,fig.width=9,fig.height=9}
library(ezmaps)
```

## generate_hexbin()

NOT DONE

```{r,fig.width=9,fig.height=9}
library(ezmaps)
```


# Session Info
```{r sessionInfo}
sessionInfo()
```

